---
output: hugodown::md_document
# Documentation: https://sourcethemes.com/academic/docs/managing-content/

title: "Using Hugodown Academic"
subtitle: ""
summary: ""
authors: []
tags: []
categories: []
date: 2020-06-27
lastmod: 2020-06-27
featured: false
draft: false

# Featured image
# To use, add an image named `featured.jpg/png` to your page's folder.
# Focal points: Smart, Center, TopLeft, Top, TopRight, Left, Right, BottomLeft, Bottom, BottomRight.
image:
  caption: ""
  focal_point: ""
  preview_only: false

# Projects (optional).
#   Associate this post with one or more of your projects.
#   Simply enter your project's folder or file name without extension.
#   E.g. `projects = ["internal-project"]` references `content/project/deep-learning/index.md`.
#   Otherwise, set `projects = []`.
projects: []
---

I'm getting attempting to get a website/blog up using hugodown and the academic theme. As a first post, I'm writing about the process of setting up the site.

I started at the [hugodown site](https://hugodown.r-lib.org/index.html) and installed hugodown

```{r, eval = FALSE}
devtools::install_github("r-lib/hugodown")
```

Then when I tried to create an academic site I got a helpful error message telling me how to install hugo first, so the next two steps are to first install hugo and then create the academic site. The `create_site_academic()` function errored out informing me that `Error: 'ui_silence' is not an exported object from 'namespace:usethis'` which was resolved by installing the latest version of `usethis` from CRAN.

```{r, eval = FALSE}
hugodown::hugo_install('0.66.0')
hugodown::create_site_academic()
```

At that point I was able to preview the default site

```{r, eval = FALSE}
hugodown::hugo_start()
```

When using the `use_post` function to create a this post I discovered it seems to set the working directory into the content folder already

```{r, eval = FALSE}
#This errors with the directory not found
hugodown::use_post("content/post/using_hugodown")

#This works
hugodown::use_post("post/using_hugodown")
```

At this point I tried knitting this post to see if the site would update and had an error of `Unknown extension: task_lists`. I tried updating `knitr` and had the same error. Next I tried installing the latest version of [pandoc](https://pandoc.org/installing.html), which worked and I was able to knit this post. Rerunning `hugo_start` showed me that the post had been added. 

```{r, eval = FALSE}
hugodown::hugo_start()
```





