---
output: hugodown::md_document
# Documentation: https://sourcethemes.com/academic/docs/managing-content/

title: "Using Hugodown Academic"
subtitle: ""
summary: ""
authors: []
tags: []
categories: []
date: 2020-06-27
lastmod: 2020-06-27
featured: false
draft: false

# Featured image
# To use, add an image named `featured.jpg/png` to your page's folder.
# Focal points: Smart, Center, TopLeft, Top, TopRight, Left, Right, BottomLeft, Bottom, BottomRight.
image:
  caption: ""
  focal_point: ""
  preview_only: false

# Projects (optional).
#   Associate this post with one or more of your projects.
#   Simply enter your project's folder or file name without extension.
#   E.g. `projects = ["internal-project"]` references `content/project/deep-learning/index.md`.
#   Otherwise, set `projects = []`.
projects: []
---

I'm getting attempting to get a website/blog up using hugodown and the academic theme. As a first post, I'm writing about the process of setting up the site.

I started at the [hugodown site](https://hugodown.r-lib.org/index.html) and installed hugodown

```{r, eval = FALSE}
devtools::install_github("r-lib/hugodown")
```

Then when I tried to create an academic site I got a helpful error message telling me how to install hugo first, so the next two steps are to first install hugo and then create the academic site. The `create_site_academic()` function errored out informing me that `Error: 'ui_silence' is not an exported object from 'namespace:usethis'` which was resolved by installing the latest version of `usethis` from CRAN.

```{r, eval = FALSE}
hugodown::hugo_install('0.66.0')
hugodown::create_site_academic()
```

At that point I was able to preview the default site

```{r, eval = FALSE}
hugodown::hugo_start()
```

When using the `use_post` function to create a this post I discovered it seems to set the working directory into the content folder already

```{r, eval = FALSE}
#This errors with the directory not found
hugodown::use_post("content/post/using_hugodown")

#This works
hugodown::use_post("post/using_hugodown")
```

At this point I tried knitting this post to see if the site would update and had an error of `Unknown extension: task_lists`. I tried updating `knitr` and had the same error. Next I tried installing the latest version of [pandoc](https://pandoc.org/installing.html), which worked and I was able to knit this post. Rerunning `hugo_start` showed me that the post had been added. 

```{r, eval = FALSE}
hugodown::hugo_start()
```

At this point I decided to work on [deploying](https://hugodown.r-lib.org/articles/deploy.html) the site.

```{r, eval = FALSE}
hugodown::use_netlify_toml()
```

I used netlify as recommended, bought my own domain name and then waited for the DNS to propogate. No issues with this part of the process. 

The next step is customizing the Academic Theme. For the most part I did this by opening up files and reading the comments. There is also [documentation](https://sourcethemes.com/academic/docs/) online. The first thing I did was work with the `content/home` folder and turn off some of the extra features. For example, if you open content/home/hero you'll be see this markdown at the top. I set active to false to get rid of the banner. 

```{r, eval = FALSE}
# Hero widget.
widget = "hero"  # See https://sourcethemes.com/academic/docs/page-builder/
headless = true  # This file represents a page section.
active = false  # Activate this widget? true/false
weight = 10  # Order that this section will appear.
```

In order to update from being Nelson Bighetti you need to look in `content/authors/admin`. By default the admin folder is linked, although if you add additional authors there is an option in `content/home/about.md` to change which author is displayed. While the initial folder structure of the academic theme is pretty overwhelming I found that just approaching it a file at a time and reading the comments let me do most of what I wanted to do. 


